---
title: "Lat/lon queries"
author: "OJ Watson"
date: '`r format(Sys.time(), ''%d %B, %Y'')`'
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: show
    css: knitr.css
    fig_caption: yes
    keep_md: yes
    theme: readable
    toc: yes
    toc_float: yes
---

## Overview
  
1. Intro
2. LatLon Examples
3. Extra

## 1. Intro

The following shows a simple way to fetch latitude/longitude coordinates for a street
address or similar using [ggmap](https://github.com/dkahle/ggmap). This package 
simply uses Google's geocoding API and thus will cap out at 2500 queries per day. 
Might be a way to spoof Google API to get round this but I haven't tried before. 

## 2. LatLon Examples

Following simply shows how to use it. 

```{r Fetch location, echo=TRUE, include=TRUE, message = FALSE, warning = FALSE}

install.packages("ggmap",repos = "https://cloud.r-project.org/")

## Then let's build a function to query google for the lat long of our location
latlon_list <- function(location){   
  
  # use the gecode function to query google servers
  geo_reply = ggmap::geocode(location, output='latlon', messaging=FALSE, override_limit=TRUE)
  
  return(list("lat"=geo_reply$lat,"lon"=geo_reply$lon))
}

## Example address
location <- "Cra. 27 #7-48, Bogotá, Colombia"

## Example use
latlon_list(location)

```

## 3. Extra

Can also get more information about the address by changing the ouput argument
to "all".

``` {r Demo, echo=TRUE, include=TRUE, message = FALSE, warning = FALSE}
str(ggmap::geocode(location, output='all', messaging=FALSE, override_limit=TRUE))
```
